```{r, echo = FALSE, warning = TRUE}

knitr::opts_knit$set(base.url = "/")
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  fig.width = 9,
  fig.height = 6
)
options(scipen = 20, digits = 2)
```

```{r}
require(dplyr)
require(tibble)
require(stringr)
```

<!DOCTYPE html>
<html>
<head>
<meta charset="UTF-8">
<link rel="stylesheet" type="text/css" href="css/bootstrap.min.css">
<link rel="stylesheet" type="text/css" href="DataTables/datatables.min.css"/>
<script type="text/javascript" src="DataTables/datatables.min.js"></script>
</head>

<body>
<script>
$(document).ready(function () {
    var table = $('table').last();
    table.children('thead').append('<tr class="name_row"></tr>');
    table.children('thead').each(function () {
        $(this).children('tr').first().attr('class', 'search_row');
    })
    $('.search_row th').each(function() {
        $(this).parent().siblings('.name_row').append($(this).clone());
        var col_text = $(this).text();
        var width = $(this).css('width');
        $th = '<div style="width: ' + width + '"><input type="text" placeholder="'+col_text+'" data-column-name="' + col_text + '"></div>';
        $(this).html($th);
    });
    var data_table = table.DataTable();
    data_table.columns().every(function () {
        var column = this;
        var header_text = $(column.header()).text();
        var $input = $('input[data-column-name="' + header_text + '"]');
        if ($('.FixedHeader_Cloned').length) {
            var $input = $('.FixedHeader_Cloned input[data-column-name="' + header_text + '"]');
        }
        $input.off('keyup change');
        $input.on('keyup change', function() {
            column.search($input.val()).draw();
        });
    });
});
</script>

<div class="container-fluid">


```{r, echo=FALSE, cache = FALSE}

journals <- readr::read_csv("combined_list.csv")

common_journals <- journals %>% filter(Catalogue == TRUE & MPG == TRUE & Netherlands == TRUE & UK == TRUE & Austria == TRUE & Sweden == TRUE & Finland == TRUE & Hungary == TRUE & Poland == TRUE)

catalogue <- journals %>% filter(Catalogue == TRUE)

count_list <- journals %>% select(Catalogue, MPG, Netherlands, UK, Austria, Sweden, Finland, Hungary, Poland) %>% summarise_all(sum) %>% add_column("Combined list" = nrow(journals))

count_list <- as_tibble(cbind(list = names(count_list), t(count_list)))

uncommon_journals <- setdiff(journals, common_journals) 

uncommon_journals_table_data <- uncommon_journals %>% select(Title, product_id, Catalogue, MPG, Netherlands, UK, Austria, Sweden, Finland, Hungary, Poland) %>% mutate(product_id = str_c("[", product_id, "](https://link.springer.com/journal/", product_id, ")"))

```

# Comparison of journal eligibility lists for Springer Compact Agreements (SCA)

## 1. Introduction

It is known that portfolios of eligible journals for the [Springer Compact Agreements](https://www.springer.com/de/open-access/springer-open-choice/springer-compact) (SCA) differ between consortional partners. 
This evaluation is meant to analyse those differences and also relate them to the full catalogue of hybrid Springer journals ("Open Choice"). Results are expected to be useful for further analyses on the effects and impacts of SCAs, like the [Coverage Analysis](https://openapc.github.io/general/openapc/2018/03/22/offsetting-coverage/) conducted by our [OpenAPC](https://github.com/OpenAPC/openapc-de) project or the impact estimations made by Jisc.

## 2. Data origins

Springer provides individual lists of eligible journals for all participants on its web site, those can be [downloaded in PDF Format](https://www.springer.com/de/open-access/springer-open-choice/springer-compact/agreements-dutch-authors) ("Click here for a list of Open Choice eligible subscription-based journals covered by the Open Access agreement with Dutch universities and Academy institutes"). 
The according files have been obtained for all consortional partners (Netherlands, UK, Sweden, Austria, Finland, Poland, Hungary and the Max Planck Society (MPG)) and can be found [here](https://github.com/cbroschinski/sca_eligible_journals_comparison/tree/master/raw_pdf_lists).
Springer also provides a full catalogue of published journals as an Excel spreadsheet which can be found [here](https://www.springernature.com/de/librarians/licensing/journals-price-list) ("2019 Springer Nature Journals including Open Access").

## 3. Data processing

Our goal was to compile a full list of Springer hybrid journals, with a set of binary variables to indicate if a journal is present in a specific sub list. The following steps were carried out:

### 3.1 PDF extraction

Since the SCA journal lists were only available in PDF format, a machine-readable variant had to be extracted first. This was done using the [Tabula](https://tabula.technology/) toolkit, the resulting CSV files can be found [here](https://github.com/cbroschinski/sca_eligible_journals_comparison/tree/master/extracted_csvs).

### 3.2 Catalogue filtering

The full Springer journal catalogue contains both fully OA and hybrid journals. Since only the latter are relevant to the SCA programme, the table was filtered, keeping only those entries with the value "Hybrid (Open Choice)" in the "open access" column. The spreadsheet was then exported to CSV (Catalogue.csv).

### 3.3 Creation of a combined list

A python [preprocessing script](https://github.com/cbroschinski/sca_eligible_journals_comparison/blob/master/preprocessing.py) creates a [combined, duplicate-free list](https://github.com/cbroschinski/sca_eligible_journals_comparison/blob/master/combined_list.csv) of all journals appearing in any of the created CSV files. 
The column "product_id" serves as primary key to find matching journals, other identifiers like title or ISSNs turned out to be inconsistent between the lists. The script notifies of such cases, an attached [log file](https://github.com/cbroschinski/sca_eligible_journals_comparison/blob/master/preprocessing_log.txt) shows the output.

### 4. Analysis

The following table shows the number of journals contained in each list:

``` {r, echo=FALSE, cache = FALSE}
knitr::kable(count_list, col.names=c("journal list", "count"))
```

Out of these `r nrow(journals)` total entries, `r nrow(common_journals)` are common journals - they appear in all the SCA eligibility lists and also in the catalogue. This means that there's a set of `r nrow(uncommon_journals)` journals which are missing in at least one of the lists. The following interactive table shows those journals and the list they are (not) part of. 
The list may be filtered to certain combinations by entering TRUE oder FALSE into the search fields above the column headers. The entry in the product_id column links to the journal landing page on SpringerLink for easy reference.

``` {r, echo=FALSE, cache = FALSE}
knitr::kable(uncommon_journals_table_data, col.names=c("Title", "product_id", "Catalogue", "MPG", "Netherlands", "UK", "Austria", "Sweden", "Finland", "Hungary", "Poland"))
```

### 5. Results

Key insights from the filtering table are:

- There are significant differences both between the eligibility lists and the catalogue. 
- The combined list consists of `r nrow(journals)` entries, which is surprising, as the list of hybrid journals filtered from the Springer catalogue only contains `r nrow(catalogue)` entries - there are `r nrow(journals) - nrow(catalogue)` journals which appear in some of the SCA eligibility lists, but not in the official catalogue. 
A closer investigation reveals that a lot of those cases are related to journals having been transferred to other publishers in the beginning of 2019. This indicates that the eligibility lists are not updated frequently (or not at all?).
- The Swedish, Hungarian, Polish and Finnish eligibilty lists are identical. While the latter cases can be explained with a common start date (They all came into effect in 2019), it is unclear why they are identical to the Swedish list, with the corresponding SCA already running since 2016. It seems as if the Swedish list was used as a template for the new SCAs.

</div>
</body>
</html>
